QPLIB: A Library of Quadratic Programming Instances

### 2018-02-08 QPLIB-3.tex
revise repetitive paragraph on not-reformulating
- format to form
- other minor fixes

\textcolor{red}{
One of the nontrivial choices in our library is that we made no effort to reformulate the instances, and inserted them in the library in the very same format they have been provided to us by the original contributors. Section \ref{ssec:reform} is crucial in justifying this choice, as it shows that there are several degrees of freedom to move the instances from one class to another. Tailoring the structure of a problem to the solver is, however, a bias we do not want to add.
}

>>>>

\textcolor{red}{
One of the nontrivial choices in our library is that we made no effort to reformulate the instances, and inserted them in the library in the very same form as they have been provided to us by the original contributors. Section \ref{ssec:reform} is crucial in justifying this choice, as it shows that there are several degrees of freedom to move the instances from one class to another. Tailoring the structure of a problem to a solver is, however, a bias that we did not want to add.
}
